\subsection{Semantic analysis of tweets} %Lisa
\label{semtanticAnalysation}
To further improve the ranking in FeedJam it would be possible to include elements of semantic technology. There are different things that can be done.

We could build user models of the users. Link the model to other social networks such as FaceBook or LinkedIn. With information collected from these places it might be possible to infer if the user tweets about something that really interests her or its about something else. An assumption would be that a user tweeting about something that interests them are more important than just posting something random. An example using LinkedIn: Through linked in it is possible to retrieve information about the persons profession and their experience and skills. Based on the content of the tweet linked with LinkedIn info about the user you could infer if the user knows the stuff she's tweeting about. 

Make ontologies of users and ontologies for tweets. Align the ontologies and reason over them. It could be possible to find related tweets about related topics. 



\subsection{Mobile Application}
Another point of future development/research would be to make the FeedJam webapplication into a mobile application for modern mobile operating systems such as iOS, Android and Windows Phone 7. There are several different ways of achieving this. 

One way would be to rewrite/cross-compile our current Spring application and rewrite the views in order to create a fully native mobile application for each operating system. There are however several difficulties with choosing this path. For instance the pagerank algorithm would probably be too taxing for the limited hardware of these devices. In addition we would be unable to distribute the collection of users, resulting in a severely limited application due to the Twitter API limitations outlined in \ref{twitterProblem}.

Another way of creating a mobile application would in essence be to rewrite the views. Through wrapping the current Javascript/jQuery logic and a new design into for instance Apache Cordova, a tool for wrapping HTML5/Javascript/CSS applications in a native web view on smart phones/tabets \cite{ApacheCordova}, we would be able to use the same controllers and models as the current web application. While this approach would require more of our web server we would be able to serve a sentralised database of UserRanks in addition to having a centralised database of Twitter users which in turn would reduce the number of requests required to do one search in the Twitter database.

\subsection{Clustering of search results and/or the cached collection} %snorre
\citet[pg. 286]{Baeza-Yates2010b} defines text clustering as, ``\textit{[\dots]given a collection D of documents, a text clustering method automatically separates these documents into K clusters according to some predefined criteria}''. Clustering algorithms are one type of text classification algorithms which can be divided into two main categories, unsupervised and supervised text classification algorithms. Clustering algorithms falls under the unsupervised category as they do not use any artificial intelligence techniques to classify the text. The predefined criteria varies between different clustering algorithm, and some clustering algorithms produce distinct clusters while others produce overlapping clusters. Generally speaking, a clustering algorithm will split a document collection into groups of documents with matching text content.

Several clustering algorithms exist such as K-means clustering, hierarchical agglomerative clustering, suffix tree clustering, etc. \cite{Baeza-Yates2010b} Clustering is not only applicable to collections of large text documents, but could also be used to cluster Tweets. Two possible clustering research problems could be worth investigating in context of the FeedJam service. The first research problem could be how we could use clustering techniques to cluster the search results. A possible scenario here would be to allow searches with for example 100 search results. These results could then be clustered and presented to the user in a visual cluster with some sort of label.

Another possible research problem could be wether one could cluster and label users based on their tweets, and then apply these clusters to the ranking algorithm. One could then regard a user as a document built up of all the user's tweets. A user could then be given a higher score if he or she is a member of a cluster with a high user rank and conversely a lower score if a member of a cluster with a low user rank. The user rank would then take into account wether a user writes about the same things as other highly ranked users.


\subsection{Permalinks for accessibility}
One major problem with FeedJam in its current iteration is the lack of permalinks. Permalinks are, as the name implies, permanent urls to specific content pages. Since we use Javascript the generation of such permalinks is not automatic due to the fact that we dynamically insert content into an already generated page. While it would not necessarily be hard to implement a permalink structure we would have to rewrite portions of both our database (in order to store tweets so that they are accessible at a later date) in addition to rewriting a large portion of the already existing Javascript.